Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-12-17 paper/authors.tex
update contact author emails

\author[LSST Dark Energy Science Collaboration]{
\parbox{\textwidth}{
\Large
S.J.~Schmidt$^{1}$,
A.I.~Malz$^{2,3,4}$,
J.Y.H.~Soo$^{5,6}$,
I.A.~Almosallam$^{7,8}$,
M.~Brescia$^{9}$,
S.~Cavuoti$^{9,10}$,
J.~Cohen-Tanugi$^{11}$,
A.J.~Connolly$^{12}$,
J.~DeRose$^{13,14,15,16,17}$,
P.E.~Freeman$^{18}$,
M.L.~Graham$^{12}$,
K.G.~Iyer$^{19,20}$,
M.J.~Jarvis$^{21,22}$,
J.B.~Kalmbach$^{12}$,
E.~Kovacs$^{23}$,
A.B.~Lee$^{18}$,
G.~Longo$^{10}$,
C.B.~Morrison$^{12}$,
J.A.~Newman$^{24}$,
E.~Nourbakhsh$^{1}$,
E.~Nuss$^{11}$,
T.~Pospisil$^{18}$,
H.~Tranin$^{11}$,
R.H.~Wechsler$^{25,16,26}$,
R.~Zhou$^{15,24}$,
R.~Izbicki$^{27,28}$,
and The LSST Dark Energy Science Collaboration
}
\vspace{0.4cm}
\\
\parbox{\textwidth}{
(Affiliations are listed at the end of the paper)
\vspace{0.8cm}
}
}

>>>>

\author[LSST Dark Energy Science Collaboration]{
\parbox{\textwidth}{
\Large
S.J.~Schmidt$^{1}$\thanks{Email: sschmidt@physics.ucdavis.edu},
A.I.~Malz$^{2,3,4}$\thanks{Email: aimalz@astro.ruhr-uni-bochum.de},
J.Y.H.~Soo$^{5,6}$,
I.A.~Almosallam$^{7,8}$,
M.~Brescia$^{9}$,
S.~Cavuoti$^{9,10}$,
J.~Cohen-Tanugi$^{11}$,
A.J.~Connolly$^{12}$,
J.~DeRose$^{13,14,15,16,17}$,
P.E.~Freeman$^{18}$,
M.L.~Graham$^{12}$,
K.G.~Iyer$^{19,20}$,
M.J.~Jarvis$^{21,22}$,
J.B.~Kalmbach$^{12}$,
E.~Kovacs$^{23}$,
A.B.~Lee$^{18}$,
G.~Longo$^{10}$,
C.B.~Morrison$^{12}$,
J.A.~Newman$^{24}$,
E.~Nourbakhsh$^{1}$,
E.~Nuss$^{11}$,
T.~Pospisil$^{18}$,
H.~Tranin$^{11}$,
R.H.~Wechsler$^{25,16,26}$,
R.~Zhou$^{15,24}$,
R.~Izbicki$^{27,28}$,
and The LSST Dark Energy Science Collaboration
}
\vspace{0.4cm}
\\
\parbox{\textwidth}{
(Affiliations are listed at the end of the paper)
\vspace{0.8cm}
}
}
